
% cryptographic program verification
Cryptographic programs are ubiquitous. They are fundamental to
computer security and deployed in numerous computer systems. It would
be disastrous if unintended behaviors could be observed in such
critical programs. In order to address this concern, several research
projects have been working on verifying cryptographic programs in
recent years~\cite{}.

% cryptoline

% overview of the parts with certification holes. 


% importance of improving the trustworth, eliminate trusted bases
% importance of keep the usability simultaneously

% ways to improve cryptoline trustworth
% smt bitvector, handy but...

More specifically, only two types of queries are produced by
\cryptoline. For range properties, over- and under-flow checking, the
tool exploits the bit vector theory in SMT (Satisfiability Modulo
Theories) solving. It invokes an SMT solver to resolve such
queries. For algebraic properties, \cryptoline reduces the
verification problem to the ideal membership problem. It then employs
a computer algebra system to resolve these queries. Correctness of the
verification tool heavily relies on correctness of the external
solvers. If an external solver reports an incorrect query
result, \cryptoline will give an unsound verification result on
cryptographic programs. In this paper, we reduce the trust base
of \cryptoline in order to improve the quality of verification
results.

% polynomial checker? short contents

% contribution

% related works

